Results from the deep learning challenge associated with the 3MD4040 lecture on plankton classification

### 2022-05-06 Report/paper.tex
page break before the appendix
fix confusion matrix legend

\begin{figure}
	\begin{tabular}{ccccc}
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_spongebob.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_cestquilepatron.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_deepwhale.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_granderegazzoni.png}&
        \includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_TheBackpropagatedStubborns.png}\\
		SpongeBob & C'est qui l'patron & DeepWhalfigs/e & GrandeRegazzoni & The Backpropagated Stubborns\\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_MetzDreamDeep.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_voleursDhuile.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_JMBmc.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_AG0D.png}&
        \includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_ResMetz.png}\\
		Metz Dream Deep & Voleurs d'Huile & JMBmcfigs/ & AG0D\\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_CelestineFeuillat.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_LesJongleurs.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_DeepBeru'4s.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_TheWhaleSharks.png}&\\
		CelestineFeuillat & LesJongleurs & DeepBeru'4s & TheWhaleSharks & 
	\end{tabular}
	\caption{\label{fig:confusion} Confusion matrices of the best submissions of all the participants.}
\end{figure}

@@

%-----------------------------------------------------------------------------------
\appendix

>>>>

\begin{figure}
	\begin{tabular}{ccccc}
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_spongebob.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_cestquilepatron.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_deepwhale.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_granderegazzoni.png}&
        \includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_TheBackpropagatedStubborns.png}\\
		SpongeBob & C'est qui l'patron & DeepWhale & GrandeRegazzoni & The Backpropagated Stubborns\\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_MetzDreamDeep.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_voleursDhuile.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_JMBmc.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_AG0D.png}&
        \includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_ResMetz.png}\\
        Metz Dream Deep & Voleurs d'Huile & JMBmc & AG0D & ResMetz \\
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_CelestineFeuillat.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_LesJongleurs.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_DeepBeru'4s.png}&
		\includegraphics[width=0.18\columnwidth]{figs/confusion_matrix_TheWhaleSharks.png}&\\
		CelestineFeuillat & LesJongleurs & DeepBeru'4s & TheWhaleSharks & 
	\end{tabular}
	\caption{\label{fig:confusion} Confusion matrices of the best submissions of all the participants.}
\end{figure}

@@

%-----------------------------------------------------------------------------------
\clearpage

\appendix
